ECON 21320: Final Paper

### 2019-03-16 Paper.Rmd
paper commit

# Abstract
[@aliprantisBlowingItKnocking2015]

>>>>

# Abstract

This paper evaluates San Francisco's Affordable Housing Program by estimating the impact of affordable developments on the assessed and predicted home values of nearby properties. We use a unique dataset constructed from detailed parcel-level tax assessment data, American Community Survey microdata, and price estimates scraped from real estate listing service Zillow. Using a difference-in-differences model, we estimate that properties with

[@aliprantisBlowingItKnocking2015]
